Syntax and Semantics of Abstract Binding Trees

### 2015-12-31 paper.tex
clarify valences over which sorts (#42)

A metavariable context consists of bindings of \emph{valences} to
metavariables; let $\Define{\Valences}{\MkSet{v\mid \IsValenceUnmoded{v}}}$ be the set
of valences. Then, the category of metavariable contexts is the comma
construction $\MCtx$, which likewise admits an equivalent inductive definition:
\begin{gather*}
  \infer{
    \IsMetaCtx{\cdot}
  }{
  }
\qquad
  \infer{
    \IsMetaCtx{\Theta,\MV{m}:v}
  }{
    \IsMetaCtx{\Theta}
&
    \IsValence{v}
&
    \NotIn{\MV{m}}{\Dom\Theta}
  }
\end{gather*}

>>>>

A metavariable context consists of bindings of $\Sorts$-\emph{valences} to
metavariables; let $\Define{\Valences}{\MkSet{v\mid \IsValenceUnmoded{v}}}$ be the set
of valences. Then, the category of metavariable contexts is the comma
construction $\MCtx$, which likewise admits an equivalent inductive definition:
\begin{gather*}
  \infer{
    \IsMetaCtx{\cdot}
  }{
  }
\qquad
  \infer{
    \IsMetaCtx{\Theta,\MV{m}:v}
  }{
    \IsMetaCtx{\Theta}
&
    \IsValence{v}
&
    \NotIn{\MV{m}}{\Dom\Theta}
  }
\end{gather*}
